<!--  Author: Daniel Kaplan -->
<!--  Subject:  -->

```{r include = FALSE}
library(mosaic)
library(statisticalModeling)
library(MultipleChoice)
tutorial::go_interactive()
```

Given data and a model design, the computer will find the model function and model values for you.  As an example, consider the Current Population Survey  data `mosaicData::CPS85`.  Suppose you want to build a model with `wage` as a response variable and `age` and `sex` as explanatory variables incorporated as main terms.  Also include the intercept term, as usual.

The two arguments to `lm()` are:

#. the model design, expressed as a formula: `wage` ~ 1 + `age` + `sex`.
#. the data to be used: `data = CPS85`  

```{r }
data(CPS85, package = "mosaicData")
mod1 <- lm( wage ~ 1 + age + sex, data = CPS85)
```




The `mod1 <- `... part of the command simply gives the model a
name so that you can use it later on.  If you construct more than one
model, it makes sense to give them different names. 

In making a graph of the function, the model values will always be plotted on the vertical axis.  But you have a choice of what to put on the horizontal axis.  This plot puts the quantitative variable `age` on the x-axis, and uses color for `sex`.

```{r echo = FALSE}
fmodel(mod1, ~ age + sex)
```

You could arrange things the other way as well.
```{r, echo = FALSE}
fmodel(mod1, ~ sex + age)
```

Note that the line in this plot is merely to guide the eye. The `sex` variable is categorical and so it's meaningless to interpolate between values.

Your task ... re-create each of the above graphs using the `fmodel()` command. The two arguments to `fmodel()` are

1. The model object itself, in this case `mod1`.
2. A formula describing which roles the explanatory variable will play in the plot, e.g. `~ age + sex` or `~ sex + age`.

```{r ex="create_a", type="pre-exercise-code"}
b <- 5
```

```{r ex="create_a", type="sample-code"}
# Create a variable a, equal to 5


# Print out a

```

```{r ex="create_a", type="solution"}
# Create a variable a, equal to 5
a <- 5

# Print out a
a
```

```{r ex="create_a", type="sct"}
test_object("a")
test_output_contains("a", incorrect_msg = "Make sure to print `a`.")
success_msg("Great!")
```


