---
title: "Graphics on Multiple Variables"
author: "Daniel Kaplan"
date: "2008"
output: html_document
runtime: shiny
---

```{r include = FALSE}
library(MultipleChoice)
# Scorekeeper <<- list(problem=NULL, attempts=NULL, score=NULL)
```


The graphic (from the New York *Times*, April 17, 2008) shows the 
fitted values from a model of the survival of babies born extremely prematurely.

<!-- TEX COMMAND NOT FOUND graphicsfile babylarge.jpg  -->
<!-- begin tabular
 ../Figures/babylarge-2.jpg TEX COMMAND NOT FOUND   
 ../Figures/babylarge-1.jpg TEX COMMAND NOT FOUND   
<!-- end tabular --> -->


<!-- begin quotation -->

*Caption: "A new study finds that doctors could better
estimate an extremely premature baby's chance of survival by
considering factors including birth weight, length of gestation, sex
and whether the mother was given steroids to help develop the baby's lungs."*
<!-- end quotation -->


Two different response variables are plotted: (1) the probability of survival 
and (2) the probability of survival without moderate to severe disabilities.
Remarkably for a statistical graphic, there are three explanatory variables:
<!-- begin enumerate -->

#. Birth weight (measured in pounds (lb) in the graphic).
<!--  #. Whether the birth was a single baby or involved multiple babies. -->
#. The sex of the baby.
#. Whether the mother took steroids intended to help the fetus's lungs develop.  
<!-- end enumerate -->

Focus on the survival rates without disabilities --- the darker bars in
the graphic.

<!-- begin enumerate -->


### Question 1

Estimate the effect of giving steroids, that is, how much extra
survival probability is associated with giving steroids?
<!-- begin MultipleChoice -->

a. No extra survival probability with steroids.
b. About 1-5 percentage points
c. RIGHT About 10 to 15 percentage points
d. About 50 percentage points
e. About 75 percentage points
<!-- end MultipleChoice -->

```{r echo = FALSE}
id1 <- "C06-S2008-101-1" # not just the value, but the variable
                         # name needs to be unique.
MC_question(id1, 
            a = "not right",
            b = "still not right",
            c = "yes, that's it.",
            d = "sorry, man",
            e = "last chance")
callModule(MC, id1, id1,
           hints = ifelse(exists("show_hints"), show_hints, FALSE ))
```


### Question 2

For the babies where the mother was given steroids, how does the
survival probability depend on the birth weight of the baby:


a. No dependence.
b. Increases by about 25 percentage points.
c. Increases by about 50 percentage points.
d. Increases by about 25 percentage points per pound.
e. RIGHT Increases by about 50 percentage points per pound.


```{r echo = FALSE}
id2 <- "C06-S2008-101-2"
MC_question(id2, 
            a = "not right",
            b = "still not right",
            c = "no, that's not it.",
            d = "sorry, man",
            e = "**RIGHT**")
callModule(MC, id2, id2,
           hints = ifelse(exists("show_hints"), show_hints, FALSE ))
```


### Question 3

For the babies where the mother was given steroids, how does the
survival probability depend on the sex of the baby?

a. No dependence.
b. RIGHT Higher for girls by about 15 percentage points.
c. Higher for boys by about 20 percentage points.
d. Higher for girls by about 40 percentage points.
e. Higher for boys by about 40 percentage points.

```{r echo = FALSE}
id3 <- "C06-S2008-101-3"
MC_question(id3, 
            a = "not right",
            b = "**RIGHT**",
            c = "no, that's not it.",
            d = "sorry, man",
            e = "last chance")
callModule(MC, id3, id3,
           hints = ifelse(exists("show_hints"), show_hints, FALSE ))
```


### Question 4

How would you look for an interaction between birth weight and baby's sex in accounting for survival?

a. Compare survival of males to females at a given weight.
b. Compare survival of males across different weights.
c. Compare survival of females across different weights.
d. RIGHT Compare the difference in survival between males and females across different weights.

```{r echo = FALSE}
id4 <- "C06-S2008-101-4"
MC_question(id4, 
            a = "not right",
            b = "still not right",
            c = "no, that's not it.",
            d = "**RIGHT**")
callModule(MC, id4, id4,
           hints = ifelse(exists("show_hints"), show_hints, FALSE ))
```


### Question 5

Do you see signs of a substantial interaction between birth
weight and sex in accounting for survival?  (Take substantial to
mean "greater than 10 percentage points.") 

```{r echo = FALSE}
id5 <- "C06-S2008-101-5"
MC_question(id5, 
            yes = "**WRONG**",
            no  = "**RIGHT**")
callModule(MC, id5, id5,
           hints = ifelse(exists("show_hints"), show_hints, FALSE ))
```

### Question 6

How would you look for a substantial interaction between steroid use and baby's sex in accounting for survival. 

a. Compare survival of males to females when the mother was given steroids.
b. Compare survival of males between steroid given and steroid not
  given.
c. Compare survival of females between steroid given and steroid
  not given.
d. RIGHT Compare the difference in survival between males and females
  between steroid given and steroid not given.

```{r echo = FALSE}
id6 <- "C06-S2008-101-6"
MC_question(id6, 
            a = "not right",
            b = "still not right",
            c = "no, that's not it.",
            d = "**RIGHT**")
callModule(MC, id6, id6,
           hints = ifelse(exists("show_hints"), show_hints, FALSE ))
```


### Question 7

Do you see signs of a substantial interaction between steroid use and sex in accounting for survival?  (Take substantial to mean "greater than 10 percentage points.") 

```{r echo = FALSE}
id7 <- "C06-S2008-101-7"
MC_question(id7, 
            yes = "**WRONG**",
            no  = "**RIGHT**")
callModule(MC, id7, id7,
           hints = ifelse(exists("show_hints"), show_hints, FALSE ))
```

